A Case Study in Preserving a High Energy Physics Application

### 2014-01-24 paper.tex
Added abstract and placed figures at beginning of paper.

\begin{abstract}
...
\end{abstract}

@@

In this paper, we demonstrate many of these difficulties by presenting
a case study of a high energy physics application, considered from
the perspective of preservation.  The application is presented to us
first in the form of an email that describes in prose how to install
the software and run the analysis.  We perform several successive
refinements to convert it into an executable and preservable object.
Then, we develop two techniques for observing and capturing the
dependencies associated with the system, comparing the cost of capture,
the size of the preserved object, and the flexibility of the resulting
object.  We describe how each of these techniques may interact with
a future archive of preserved software artifacts, and conclude with
some reflections on the challenges of preservation and advice for future efforts.

@@

@@

@@

@@

\begin{figure}
\centering
\epsfig{file=dependencies.eps, height=3in, width=3.5in}
\caption{Dependencies}
\label{fig:dependencies}
\end{figure}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
        \hline
        Source of Software & Size of Software \\ \hline
        cmssw\_5\_3\_11\_patch3 & 1.16TB \\ \hline
        Git & 51MB \\ \hline
        Public HTTP & 52MB \\ \hline
        Private home page & 41KB \\ \hline
    \end{tabular}
    \caption{Source and Size of Software}
    \label{table:software-source-size}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Source & Original & Referred & Really Used \\ 
        & Size & Size & Size \\ \hline
        CMSSW & 1.16TB & 449MB & 5.2MB\\ \hline
        Git & 51MB & & \\ \hline
        Public HTTP & 52MB & & \\ \hline
        Private home page & 41KB & & \\ \hline
        HDFS & 33TB & 43.3GB & 20GB \\ \hline
        pscratch & 206TB & & 119MB \\ \hline
        Local Disk & & & 88.4MB \\ \hline     
    \end{tabular}
    \caption{Really Used Data and Software Size}
    \label{table:size-original-real}
\end{table}

\begin{figure}
\centering
\epsfig{file=data-code-size.eps, height=3in, width=3.5in}
\caption{Workflow of Tau Analysis}
\label{fig:data-code-size}
\end{figure}

@@

\begin{figure*}
\centering
\epsfig{file=version-evolution.eps, height=4in, width=6.5in}
\caption{Version Evolution}
\label{fig:version-evolution}
\end{figure*}

>>>>

\begin{abstract}
\it The reproducibility of scientific results increasingly
depends upon the preservation of computational artifacts.
Although preserving a computation to be used later sounds
easy, it is surprisingly difficult due to the complexity
of existing software and systems.  Implicit dependencies,
networked resources, and shifting compatibility all conspire
to break applications that appear to work well.  To investigate
these issues, we present a case study of a complex high energy
physics application.  We analyze the application and attempt
several methods at extracting its dependencies for the purposes
of preservation.  We report on the completeness, performance,
and efficiency of each technique, and offer some guidance for
future work in application preservation.
\end{abstract}

@@

We do not claim to have solved these problems in any comprehensive
way.  Rather, our aim in this paper is to highlight the scope
of the problems by presenting a case study of one complex application.
The application is presented to us
first in the form of an email that describes in prose how to install
the software and run the analysis.  We perform several successive
refinements to convert it into an executable and preservable object.
Then, we develop two techniques for observing and capturing the
dependencies associated with the system, comparing the cost of capture,
the size of the preserved object, and the flexibility of the resulting
object.  We describe how each of these techniques may interact with
a future archive of preserved software artifacts, and conclude with
some reflections on the challenges of preservation and advice for future efforts.

@@

\begin{figure}[t]
\centering
\includegraphics[width=.8\columnwidth]{data-code-size.eps}
\caption{Inputs to Tau Analysis}
\label{fig:data-code-size}
\end{figure}

@@

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        SBEAN data    & hdfs & 33TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 1.16TB & 449MB & 5.2MB\\ \hline
        Tau source       & git & 51MB & 51MB & 51MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & hpc fs & 206TB & ??? & 119MB \\ \hline
        Linux commands & local fs & ??? & ??? & 88.4MB \\ \hline     
        Total          &          & ??? & ??? & ??? \\ \hline
    \end{tabular}
    \caption{Data and Code Used by Tau Analysis}
    \label{table:size-original-real}
\end{table}

@@

\begin{figure*}
\centering
\includegraphics[width=1.6\columnwidth]{version-evolution.eps}
\caption{Version Evolution}
\label{fig:version-evolution}
\end{figure*}

@@

@@

@@

@@
